\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,%
            left=.75in,right=.75in,top=1in,bottom=1in]{geometry}
\setlength{\headsep}{0.25in}

\usepackage{amsthm}

\usepackage{graphicx}
\usepackage{pgfplots}
            
\usepackage[english]{babel}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{case}{Case}

\usepackage{amsthm}
\usepackage{lipsum}

\makeatletter
\newcommand{\proofpart}[2]{%
  \par
  \addvspace{\medskipamount}%
  \noindent\emph{Part #1: #2}\par\nobreak
  \addvspace{\smallskipamount}%
  \@afterheading
}
\makeatother

\newcommand\restr[2]{{% we make the whole thing an ordinary symbol
  \left.\kern-\nulldelimiterspace % automatically resize the bar with \right
  #1 % the function
  \vphantom{\big|} % pretend it's a little taller at normal size
  \right|_{#2} % this is the delimiter
  }}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\usepackage{mathtools}
\DeclarePairedDelimiter\bra{\langle}{\rvert}
\DeclarePairedDelimiter\ket{\lvert}{\rangle}
\DeclarePairedDelimiterX\braket[2]{\langle}{\rangle}{#1 \delimsize\vert #2}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyhdr}

\DeclareMathOperator{\interior}{int}

\newcommand{\Tau}{\mathcal{T}}

\newenvironment{amatrix}[1]{%
  \left(\begin{array}{@{}*{#1}{c}|c@{}}
}{%
  \end{array}\right)
}

\usepackage{calligra}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\DeclareFontShape{T1}{calligra}{m}{n}{<->s*[2.2]callig15}{}

\newcommand{\scripty}[1]{\ensuremath{\mathcalligra{#1}}}

\pagestyle{fancy}
\author{Jeremiah Givens}
\newcommand{\subject}{Real Analysis I}
\newcommand{\Date}{9/2/2021} 
\makeatletter
\rhead{{\small\@author}}
\lhead{{\small\subject}}
\chead{{\large Homework 5}}
\cfoot{}
\rfoot{\thepage}
\lfoot{\today}

\renewcommand{\theequation}{\arabic{equation}}

\begin{document}
\section*{Problem 1}
\begin{theorem}
Let $|E| < \infty$ and $E_i$ $(i = 1,2,...,m)$ be measurable subsets of $E$. Let $k \in \{1,2,...,m\}$. Show that if every point of $E$ belongs to at least $k$ of $E_i$, then there is $i$ such that $|E_i| \geq \frac{k}{m}|E|$.
\end{theorem}

\subsection*{Solution}
\begin{proof}
Since each $k \leq \sum_{i = 1}^m \chi_{E_i}$ for each $k \in E$, theorem 5.5 tells us that 
\begin{align*}
\int_E k &\leq \int_E \sum_{i = 1}^m \chi_{E_i}.
\end{align*}
The left hand side of this inequality is easily evaluated to be $k|E|$ by Corollary 5.4. For the right hand side, we can use theorem 5.14 to see
\begin{align*}
\int_E \sum_{i = 1}^m \chi_{E_i} &= \sum_{i = 1}^m \int_E \chi_{E_i}\\
&= \sum_{i = 1}^m |E_i|\\
&\leq \sum_{j = 1}^m \max \{|E_i|: i = 1, 2, ..., m\}\\
&= m \cdot \max \{|E_i|: i = 1, 2, ..., m\}.
\end{align*}
Thus, we have that 
\begin{align*}
k|E| \leq m \cdot \max \{|E_i|: i = 1, 2, ..., m\} &\implies \frac{k}{m} = \max \{|E_i|: i = 1, 2, ..., m\},
\end{align*}
and our proof is complete.
\end{proof}

\section*{Problem 2}
Let $f$ be continuous and nonnegative on $[a, b]$ where $-\infty < a < b < \infty$. Define a nondecreasing sequence of step functions $\{\phi_k \}$ on $[a, b]$ such that $\phi_k \to f$ on $[a, b]$. Then,  use the monotone convergence theorem to show that
\begin{align*}
(L) \int_{[a, b]} f(x) dx = (R) \int_a^b f(x)dx.
\end{align*}

\subsection*{Solution}
Since $f$ is continuous, we have that it is Reimann integrable and Lebesgue integrable. For each $k \in \mathbb{N}$, lets create a partition of $[a, b]$, $\Gamma_k = \{I^k_1, I^k_2,...,I^k_{N_k} \}$ with norm $|\Gamma_k| <\frac{1}{k}$. For each partition, define a function $\phi_k: [a, b] \to \mathbb{R}$ such that for $x \in I^k_n$, we have
\begin{align*}
\phi_k(x) = \inf \{f(x_n): x_n \in I^k_n\}.
\end{align*}
Then, we clearly have that $\phi_k \nearrow f$. By the monotone convergence theorem, we have
\begin{align*}
(L) \int_{[a, b]} \phi_k(x)dx \to (L) \int_a^b f(x)dx.
\end{align*}
Also, we have by corollary 5.4 that
\begin{align*}
(L) \int_{[a, b]} \phi_k(x)dx = \sum_{n = 1}^{N_k} \inf \{f(x_n): x_n \in I^k_n\} \cdot |k|
\end{align*}
which is nothing more than a lower Reimann sum of $f$. Thus, we can conclude that 
\begin{align*}
(L) \int_{[a, b]} \phi_k(x)dx \to (R) \int_a^b f(x)dx,
\end{align*}
and ultimately that
\begin{align*}
(L) \int_{[a, b]} f(x) dx = (R) \int_a^b f(x)dx.
\end{align*}

\section*{Problem 3}
\begin{theorem}
Let $f \geq 0$ be measurable in $\mathbb{R}^n$. For $k=1,2,...,$, define the cut-off functions 
\[   f = \left\{
\begin{array}{ll}
      f(x) & \text{if } f(x)<k \\
      0 & \text{if } f(x) \geq k\\
\end{array} 
\right. \]

Then, (i) each $f_k$ is measurable on $\mathbb{R}^n$ and (ii)
\begin{align*}
\int_{\mathbb{R}^n} f_k(x)dx \to \int_{\mathbb{R}^n} f(x)dx
\end{align*}
as $k \to \infty$.
\end{theorem}

\subsection*{Solution}
\begin{proof}
\proofpart{(i)}{} Let $a \in \mathbb{R}$. Suppose first that $a \geq k$. Then
\begin{align*}
\{f_k > a \} &= \{x \in  \mathbb{R}: f_k(x) > a \}\\
&\subseteq \{x \in  \mathbb{R}: f_k(x) > k \}\\
&= \emptyset,
\end{align*}
and we can conclude that $\{f_k > a \} = \emptyset$, which is measurable.

Now suppose that $0 < a < k$. Then, we have
\begin{align*}
\{f_k > a \} &= \{a < f_k <k \}\\
&= \{a < f < k \},
\end{align*}
which is measurable, since $f$ is measurable. 

Now suppose that $a = 0$. Then,
\begin{align*}
\{f_k > a \} &= \{f_k > 0 \}\\
&= \{0 < f < k \} 
\end{align*}
which is measurable, since $f$ is measurable. 

Finally,  suppose that $a < 0$. Then,
\begin{align*}
\{f_k > a \} &= \{f_k \geq 0 \}\\
&= \mathbb{R}^n &&\text{Since } f_k \text{ is a nonnegative function.}
\end{align*}
Thus, in every case, $\{f_k > a \}$ is measurable, and we have shown that each $f_k$ is measurable.

\proofpart{(ii)}{} 
Since $f$ is finite a.e., theorem 5.10 in our text tells us that it will suffice to show that
\begin{align*}
\int_{E} f_k(x)dx \to \int_{E} f(x)dx,
\end{align*}
where $E \subseteq \mathbb{R}^n$ is the set of all $x \in \mathbb{R}^n$ such that $f(x)$ is finite. Since each $f_k$ is measurable and nonnegative, the monotone convergence theorem tells us that if $f_k \nearrow f$ on $E$, then we will have the desired result. Thus, we will show that $f_k \nearrow f$ on $E$. 

Let $x \in E$. Since $f$ is finite on $E$, there exists some least $K \in \mathbb{N}$ such that $f(x) < K$. Thus, for all $k \geq K$, we have that $f_k(x) = f(x)$. Now suppose that $k < K$. Then, we have $f_k(x) = 0 < f(x)$. Since this is true for any $x$, we have shown that $f_k \leq f$ for all $k$ and that $f_k \to f$. Thus, $f_k \nearrow f$, and our proof is complete.
\end{proof}

\section*{Problem 4}
\begin{theorem}
Suppose that $f \geq 0$ is continuous on $(0, 1]$ and the improper Riemann integral 
\begin{align*}
(R) \int_0^1 f(x) dx = \lim_{a \to 0^+} (R) \int_a^1 f(x) dx
\end{align*}
exists (finite or $+\infty$). Then,
\begin{align*}
(L) \int_{(0, 1]} f(x) dx = (R) \int_0^1 f(x) dx.
\end{align*}
\end{theorem}

\subsection*{Solution}
\begin{proof}
Define the sequence of functions $\{f_k \}$ by 
\begin{align*}
f_k = \chi_{[\frac{1}{k},  1]} f.
\end{align*}
Clearly, we have that $f_k \leq f$ and $f_k \to f$, and therefore that $f_k \nearrow f$.  Furthermore, since indicator functions are measurable, and $f$ is measurable, we have by theorem 4.10 that each $f_k$ is measurable. Thus, we have by the monotone convergence theorem that
\begin{align*}
(L) \int_{(0, 1]} f_k dx \to (L) \int_{(0, 1]} f dx.
\end{align*}
In addition to this, we have that for each $k$,
\begin{align*}
(L) \int_{(0, 1]} f_k dx &= (L) \int_{(0, \frac{1}{k})} f_k dx + (L) \int_{[\frac{1}{k}, 1]} f_k dx &&\text{By theorem 5.7}\\
&= 0 + (L) \int_{[\frac{1}{k}, 1]} f_k dx &&\text{Since } f_k = 0 \text{ on } (0, \frac{1}{k}) \\
&= (L) \int_{[\frac{1}{k}, 1]} f_k dx\\
&= (R) \int_{\frac{1}{k}}^1 f(x) dx &&\text{By problem 2}
\end{align*}
Thus, putting all of this together, we have
\begin{align*}
(R) \int_0^1 f(x) dx &= \lim_{k \to \infty} (R) \int_{\frac{1}{k}}^1 f(x) dx\\
&= \lim_{k \to \infty} (L) \int_{[\frac{1}{k}, 1]} f_k dx\\
&= \lim_{k \to \infty} (L) \int_{(0, 1]} f_k dx\\
&= (L) \int_{(0, 1]} f dx,
\end{align*}
and our proof is complete.
\end{proof}

\section*{Problem 5}
\begin{theorem}
Let $f$ be nonnegative and measurable on a measurable set $E \subseteq \mathbb{R}^n$ with $|E| < \infty$.
\proofpart{(i)}{} 
If $f \leq M$ a.e. on $E$ where $M > 0$ is constant, then
\begin{align*}
\int_E f &= \inf \sum_j [\sup_{x \in E_j} f(x)] |E_j|,
\end{align*}
where the infimum is taken over all decompositions $E = \bigcup_j E_j$ of $E$ into the union of a finite number of disjoint measurable sets $E_j$.

\proofpart{(ii)}{} The statement of (i) can fail if we allow $f$ to be unbounded.
\end{theorem}

\subsection*{Solution}
\begin{proof}
\proofpart{(i)}{} In light of theorem 5.10, we will assume that $f \leq M$ everywhere on $E$. Then, we have that the measurable function $M - f$ is nonnegative on $E$.  Utilizing theorem 5.8, we have
\begin{align*}
\int_E (M - f) &= \sup \sum_j [\inf_{x \in E_j} (M - f(x))]|E_j|\\
&= - \inf \left(- \sum_j [\inf_{x \in E_j} (M - f(x))]|E_j|\right) &&\text{Using the relation between inf and sup we used to prove 4.11}\\
&= - \inf \sum_j [\sup_{x \in E_j} (f(x) - M)]|E_j| &&\text{Using the same relation again}\\
&= - \inf \sum_j ([\sup_{x \in E_j} f(x)] - M)|E_j| \\
&= \inf \sum_j M|E_j| - \inf \sum_j [\sup_{x \in E_j} f(x)] |E_j| \\
&= \sum_j M|E_j| - \inf \sum_j [\sup_{x \in E_j} f(x)] |E_j| \\
&= \int_E M - \inf \sum_j [\sup_{x \in E_j} f(x)] |E_j|  &&\text{By theorem 5.7 and corollary 5.4}.
\end{align*}
We have by theorem 5.5 part (i) that $\int_E f \leq \int_E M$. Combining this with that fact $\int_E M = M|E|$, we have that the integral of $f$ is finite. Finally, using corollary 5.15, we have that 
\begin{align*}
\int_E M  - \int_E f &= \int_E (M - f)\\
&= \int_E M - \inf \sum_j [\sup_{x \in E_j} f(x)] |E_j|\\
- \int_E f &= - \inf \sum_j [\sup_{x \in E_j} f(x)] |E_j|\\
\int_E f &= \inf \sum_j [\sup_{x \in E_j} f(x)] |E_j|,
\end{align*}
and our proof of (i) is complete.

\proofpart{(ii)}{}
Consider the function $f(x) = \frac{1}{\sqrt{x}}$ with $E = (0, 1]$. Taking the limit of Reimann integrals in the same manner as problem 4 leads us easily to the fact that 
\begin{align*}
\int_{(0, 1]} f(x) dx = 2.
\end{align*}
Now, let $\{E_j \}$ be some finite decomposition of $E$ into disjoint measurable sets. Since this decomposition is finite, there must be some $E_j$ that contains an interval $(0, \epsilon)$ for some $\epsilon > 0$. Thus, we have
\begin{align*}
\sum_j [\sup_{x \in E_j} f(x)]|E_j| &\geq [\sup_{x \in (0, \epsilon)} f(x)]|(0, \epsilon)|\\
&= \infty \cdot \epsilon\\
&= \infty.
\end{align*}
Since this is true for any such decomposition, we have that
\begin{align*}
\inf \sum_j [\sup_{x \in E_j} f(x)] |E_j| &= \infty\\
&\not= \int_{(0, 1]} f(x) dx,
\end{align*}
and our proof is complete.
\end{proof}

\section*{Problem 6}
\begin{theorem}
Let $\{f_k \}$ be a sequence of nonnegative measurable functions defined on $E$. If $f_k \to f$ and $f_k \leq f$ a.e. on $E$, then 
\begin{align*}
\int_E f_k \to \int_E f.
\end{align*}
\end{theorem}

\subsection*{Solution}
\begin{proof}
Since $f_k \leq f$ a.e., we can define for each $k$ a set of measure zero
\begin{align*}
Z_k = \{f_k > f \}.
\end{align*}
With this, define $Z = \bigcup_{k=1}^\infty Z_k$. Then, $Z$ has zero measure, and we have that for each $k$, $f_k \leq f$ and $f_k \to f$ on $E - Z$. Thus,
\begin{align*}
\lim_{k \to \infty} \int_E f_k &= \lim_{k \to \infty} \left(\int_{E - Z} f_k + \int_Z f_k \right) && \text{By theorem 5.7}\\
&= \lim_{k \to \infty} \int_{E - Z} f_k &&\text{By theorem 5.9, since } |Z| = 0\\
&= \int_{E - Z} f &&\text{By the monotone convergence theorem}\\
&= \int_{E - Z} f + \int_{Z} f\\
&= \int_{E} f,
\end{align*}
and our proof is complete.
\end{proof}

\section*{Problem 7}
\begin{theorem}
If $f \in L(0, 1)$, then $x^k f(x) \in L(0, 1)$ for $k = 1,2,...,$, and 
\begin{align*}
\int_0^1 x^k f(x) dx \to 0.
\end{align*}
\end{theorem}

\subsection*{Solution}
\begin{proof}
Since $x^k$ is continuous, we have that $x^k$ is measurable. Furthermore, we have that $|x^k| = x^k \leq 1$ for all $x \in (0, 1)$. Thus, by theorem 5.30, $x^kf(x) \in L(0, 1)$ for each $k \in \mathbb{N}$.

We will now use the monotone convergence theorem (part (ii)) to show that $\int_0^1 x^k f(x) dx \to 0$.  Define $f_k = x^k f(x)$, and $\phi = |f|$. Clearly, we have that $f_k \leq \phi$ on $(0, 1)$. By theorem 5.21, we have that $\phi \in L(0, 1)$. Thus, it just remains to show that $f_k \to 0$ a.e. on $(0, 1)$.

By theorem 5.22, we have that $f(x)$ is finite for almost all $x \in (0, 1)$. Let $x \in (0, 1)$ be such that $f(x)$ is finite, and let $\epsilon > 0$.  We have that $x^k \to 0$,  thus, there exists some $K \in \mathbb{N}$ such that for all $k \geq K$, $x^k < \frac{\epsilon}{|f(x)|}$. Then, we have for all $k \geq K$,
\begin{align*}
|f_k(x)| &= |x^k f(x)|\\
&= x^k |f(x)|\\
&< \frac{\epsilon}{|f(x)|} |f(x)|\\
&= \epsilon.
\end{align*}
Thus, $f_k \to 0$ a.e. on $(0, 1)$, and the monotone convergence theorem leads us to conclude that 
\begin{align*}
\int_0^1 x^k f(x) dx \to 0,
\end{align*}
and our proof is complete.
\end{proof}

\section*{Problem 8}
\begin{theorem}
\proofpart{(a)}{} Let $\{f_k \}$ be a sequence of measurable functions on $E$. Then $\sum f_k$ converges absolutely a.e. in $E$ if $\sum \int_E |f_k| < + \infty$.

\proofpart{(b)}{} If $\{r_k\}$ denotes the rational numbers in $[0, 1]$ and $\{a_k \}$ satisfies $\sum |a_k| < \infty$, then $\sum a_k |x - r_k|^{-1/2}$ converges absolutely a.e. in $[0, 1]$.
\end{theorem}

\subsection*{Solution}
\begin{proof}
\proofpart{(a)}{} Suppose that $\sum \int_E |f_k| < + \infty$. Since each $f_k$ is measurable, we have that the nonnegative functions $|f_k|$ are measurable. Thus, by theorem 5.16, we have
\begin{align*}
\sum \int_E |f_k| &= \int_E \sum |f_k|.
\end{align*}
By theorem 5.22, we have $\int_E \sum |f_k| < \infty$ implies that $\sum |f_k|$ is finite a.e. in $E$. Thus, we have shown that $\sum |f_k|$ converges absolutely a.e. in $E$.

\proofpart{(b)}{}
We have that $|x - r_k|^{-1/2}$ is continuous and nonnegative on $[0, r_k)$ and $(r_k, 1]$, and is thus Riemann integrable on these sets.  Furthermore, by the results of Problem 4, the Riemann integral coincides with the Lebesgue integral on these sets. Thus, we have
\begin{align*}
\int_{[0, 1]} a_k |x - r_k|^{-1/2} dx &= \int_{[0, r_k)} a_k |x - r_k|^{-1/2}  + \int_{(r_k, 1]} a_k |x - r_k|^{-1/2} dx\\
&= \int_{[0, r_k)} a_k (r_k - x)^{-1/2}  + \int_{(r_k, 1]} a_k (x - r_k)^{-1/2} dx\\
&= (R) \int_0^{r_k} a_k (r_k - x)^{-1/2}  + (R) \int_{r_k}^1 a_k (x - r_k)^{-1/2} dx.
\end{align*}

Using the standard techniques from elementary real analysis (u substitution), we have
\begin{align*}
(R) \int_0^{r_k} a_k (r_k - x)^{-1/2} &= 2a_k r^{1/2},
\end{align*}
and
\begin{align*}
(R) \int_{r_k}^1 a_k (x - r_k)^{-1/2} dx &= 2a_k (1 - r_k)^{1/2}.
\end{align*}
With this, we have
\begin{align*}
\int_{[0, 1]} a_k |x - r_k|^{-1/2} dx &= 2a_k r_k^{1/2} + 2a_k (1 - r_k)^{1/2}\\
&= 2a_k(r_k^{1/2} + (1 - r_k)^{1/2})\\
&\leq 4 a_k.
\end{align*}
Finally, we have
\begin{align*}
\sum_k \int_{[0, 1]} |a_k| |x - r_k|^{-1/2} dx &\leq \sum_k 4 |a_k|\\
&= 4 \sum_k |a_k|\\
&< \infty.
\end{align*}
By part (a), we have shown that $\sum a_k |x - r_k|^{-1/2}$ converges absolutely a.e. in $[0, 1]$.
\end{proof}
\end{document}